---
title: "Homework 5"
author: "Suning Zhao"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. This was not prepared as a GitHub repo.

```{r load_libraries}
library(tidyverse)
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

The code chunk below imports the data from github website. To do this, I create a dataframe that includes 

```{r}
homicides_raw_df = 
  read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city,state,sep=",")
  ) 
```

```{r}
homicides_total_df =
  homicides_raw_df %>%  
  group_by(city_state) %>%
  summarize(
    n_homicides = n()  
    ) 

homicides_unsolved_df =
  homicides_raw_df %>%
  filter(disposition != "Closed by arrest") %>% 
  group_by(city_state) %>%
  summarize(
    n_homicides_unsolved = n()  
    ) 

homicides_count_df = 
  full_join(homicides_total_df, homicides_unsolved_df) 

homicides_count_df %>% 
  knitr::kable(digits = 3) 
```

```{r}
baltimore_count_df = 
  homicides_count_df %>% 
  filter(city_state == "Baltimore,MD")

prop_test = 
  prop.test(
    x = baltimore_count_df %>% pull(n_homicides_unsolved), 
    n = baltimore_count_df %>% pull(n_homicides)) 

baltimore_prop_df = broom::tidy(prop_test)

baltimore_prop_df %>% 
  select(estimate, conf.low, conf.high) 
```



## Problem 3


